The landscape of chloroplast genome assembly tools

### 2019-06-09 manuscript/bmc_article.tex
Update on Overleaf.

\usepackage{xr}
\externaldocument{supplement}

@@

Not all the tools were able to benefit from having access to multiple threads. Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads. \cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu}).

\subsubsection*{Memory and CPU Usage }
The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
The number of allowed threads had only a limited impact on the peak memory usage.
Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
In contrast, the disk usage is independent from input size and number of threads for all assemblers.
%but the factor between the programs exceeds a factor of \num{100}.

@@

\section*{Additional Files}
  \subsection*{Additional file 1 --- supplemental data}
  Supplementary data contain a complete list of all real data sets used in this study. Additionally, a table with more details to the used docker images and the detailed results of the performance measurement are included. The file is available at \cite{supplement}.

>>>>

\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
\myexternaldocument{supplement}

@@

Not all the tools were able to benefit from having access to multiple threads. Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads. \cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).

\subsubsection*{Memory and CPU Usage }
The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
The number of allowed threads had only a limited impact on the peak memory usage.
Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
In contrast, the disk usage is independent from input size and number of threads for all assemblers.
%but the factor between the programs exceeds a factor of \num{100}.

@@

\section*{Additional Files}
  \subsection*{Additional file 1 --- supplemental data}
  Supplementary data contain a complete list of all real data sets used in this study. Additionally, a table with more details to the used docker images and the detailed results of the performance measurement are included. The file is available at \cite{zenodosupplement}.
